Concurrent Programming with CXL

### 2020-06-05 book/paper.tex
Latest
Fixed a few small things

@@

So far we have looked at how to protect a single resource.  Sometimes
we have multiple but a limited amount of resources that require
protection.  That is, if there are only $n$ resources, no more than
$n$ can be used at a time; if all are in use and a process come along
that needs one of the resources, it has to wait until another process
releases one of the resources.  Note that we cannot solve this problem
simply using a lock per resource---allocating a resource requires access
to all of them.

@@

Introduced by the famous Dutch computer scientist Edsger Dijkstra,
a \emph{semaphore} is a primitive that fits the bill.  A semaphore is essentially
a counter that can be incremented and decremented but is not allowed to go
below zero.  The semaphore counter is typically initialized to the number of
resources available.  When allocating a resource, a process decrements the
counter using the \texttt{procure} or simply \texttt{P} operation.  The
\texttt{procure} operation blocks the invoking process if the counter is zero.
To release the resource, a process increments the resource using the
\texttt{vacate} or {V} operation.
Figure~\ref{fig:semaphore} shows the \texttt{synch} module implementation of
semaphores.

>>>>

\begin{quote}
\begin{itemize}
\item Is Peterson's Algorithm blocking or busy-waiting?
\item Check your answer by developing a test.
\end{itemize}
\end{quote}

@@

So far we have looked at how to protect a single resource.
Some types of resources may have multiple units or slots, each of which
If there are only $n$ units, no more than $n$ units can be used at a time;
if all are in use and a process comes along that needs one of the units,
it has to wait until another process releases one of the units.
Note that we cannot solve this problem simply using a lock per unit---allocating
a unit requires access to the entire collection.

@@

Introduced by the famous Dutch computer scientist Edsger Dijkstra,
a \emph{semaphore} is a primitive that fits the bill.  A semaphore is essentially
a counter that can be incremented and decremented but is not allowed to go
below zero.  The semaphore counter is typically initialized to the number of
units of a resource initially available.
When allocating a resource, a process decrements the
counter using the \texttt{procure} or simply \texttt{P} operation.  The
\texttt{procure} operation blocks the invoking process if the counter is zero.
To release the resource, a process increments the resource using the
\texttt{vacate} or {V} operation.
Figure~\ref{fig:semaphore} shows the \texttt{synch} module implementation of
semaphores.
